\chapter{Conclusion and Future work}
This chapter will conclude the thesis and will provide directions for the future work that can be carried out in the field.
\section{Conclusion}
To conclude, we can say that technology is changing at an alarming rate. Service providers want to catch up with the technology advances and address the privacy issues currently prevalent. But it is not easy as they are not yet ready to give up on the legacy systems. Also, its difficult to make radical changes in already running systems. 

Service providers still rely on the user data they have stored to provide their services and it is difficult to remove that reliability at once. These changes cannot be made overnight but it will take some time for the industry to understand the value in changing their business processes to not to rely that much on the user data. 
\section{Future Work}
Providing anonymity in business processes is an interesting field of research, both for the industry and academic point of view. This section provides some insights on how the systems presented in the thesis may affect future research in the area and how it can be used in some alternate ways by the industry.
\subsection{Reidentification possibilities}
In our sytems we have removed the identification from the transactions. As mentioned in \cite{de2015unique} the researchers were able to reidentify individuals based on the credit card transactions from the past three months, even though all those transactions were completely anonymized. It would be interesting to put our system into place and use the same methodology to see if the individuals can be reidentified.
\subsection{Providing services using the third party}
One more aspect, as we see from our point of view, is that our system has removed the identity from the the service part of the businesses. As most of the businesses are moving towards outsourcing their IT divisions for cost-cutting purposes, our system provides them a unique opportunity to do so. As there is no identity involved in the service system, the whole service side can be outsourced without the risk of giving away confidential data to the third parties.

This chapter concluded the thesis and provided some insights on future work that can be done in the field.

